INLA two dimensional grid replication

### 2022-09-29 src/example_inla-grid/inla-grid.Rmd
Add .pdf of inla-grid

ggplot() +
  geom_point(data = theta_grid, aes(x = theta1, y = theta2), alpha = 0.5) +
  geom_contour(data = ground_truth, aes(x = theta1, y = theta2, z = pdf), col = multi.utils::cbpalette()[1]) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend, colour = as.factor(pc)),
               data = segments, size = 1, arrow = arrow(length = unit(0.3, "inches")),
               lineend = "round", linejoin = "round") +
  scale_colour_manual(values = multi.utils::cbpalette()[-1]) +
  labs(x = "theta1", y = "theta2") +
  theme_minimal() +
  theme(legend.position = "none")
```

>>>>

plot <- ggplot() +
  geom_point(data = theta_grid, aes(x = theta1, y = theta2), alpha = 0.5) +
  geom_contour(data = ground_truth, aes(x = theta1, y = theta2, z = pdf), col = multi.utils::cbpalette()[1]) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend, colour = as.factor(pc)),
               data = segments, size = 1, arrow = arrow(length = unit(0.3, "inches")),
               lineend = "round", linejoin = "round") +
  scale_colour_manual(values = multi.utils::cbpalette()[-1]) +
  labs(x = "theta1", y = "theta2") +
  theme_minimal() +
  theme(legend.position = "none")

plot
```

```{r}
pdf("inla-grid.pdf", h = 4.5, w = 6.25)

plot

dev.off()
```
